### 2017-10-23 paper/sections/1_introduction.tex
paper: patrick feedback and spellcheck
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%\begin{table}
%\begin{tabular}{ r | l }
%  Subtree         & Example \\\hline
%  (1)   & \{Index, Batch\}FS~\cite{ren:sc2014-indexfs, zheng:pdsw2014-batchfs} \\
%  (2)   & \{Index, Ceph\}FS~\cite{ren:sc2014-indexfs, weil:sc2004-dyn-metadata} \\
%  (3)   & RAMDisk \\
%  (4)   & DeltaFS~\cite{zheng:pdsw2015-deltafs} \\
%\end{tabular}
%
%\caption{State-of-the-art systems in HPC improve file system metadata
%performance by relaxing consistency and durability guarantees. Note that
%IndexFS also supports weak consistency with bulk inserts.
%\label{table:namespaces}} \end{table}

@@

  \item A framework and API for assigning consistency/durability policies 
  to subtrees in the file system namespace; this lets users navigate
  the tradeoffs of different metadata protocols.

>>>>

@@

  \item A framework and API for assigning consistency/durability policies 
  to subtrees in the file system namespace; this lets users navigate
  the trade-offs of different metadata protocols.

### 2017-10-23 paper/sections/3_posix_overheads.tex
paper: patrick feedback and spellcheck
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many
creates, has the highest resource usage which suggests that it is stressing the
consistency and journaling subsystems of the metadata server the most.
Traditional file system techniques for improving performance, such as caching
inodes, do not help for create-heavy workloads.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-journal.png}
      \caption{Runtime normalized to no journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-interfere.png}
      \caption{Interference forces \texttt{lookup()}s}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{Interference hurts variability}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{The overhead of global durability and strong consistency in CephFS.
  (a) shows the effect of different journal segment sizes, which are streamed
  into the object store for fault tolerance. (b) and (c) show that when a second
  client ``interferes", capabilities are revoked and metadata servers do more
  work.  \label{fig:overhead}}
\end{figure*}

% what is durability
While durability is not specified by POSIX IO, users expect that files they create
or modify survive failures.  We define three types of durability: global,
local, and none.  Global
durability means that the client or server can fail at any time and metadata
will not be lost. Local durability means that metadata can be lost if the
client or server stays down after a failure. None means that metadata is volatile
and that the system provides no guarantees when clients or servers fail. 
None is different than local durability because regardless of the type failure,
metadata will be lost when components die in a None configuration.

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to grow to large which
ensures (1) sequential writes into the object store and (2) the ability for daemons to
trim redundant or irrelevant journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. Unless the journal saturates 
memory or CPU resources, larger values for these tunables results in better
performance.

@@

\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
to the best of our knowledge, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then, on restart,
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which
initially reside in memory but are later flushed to the underlying
distributed file system.

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:overhead-b}.  If only one client is creating files in a
directory (``isolated" curve on \(y1\) axis) then that client can lookup the
existence of new files locally before issuing a create request to the metadata
server. If another client starts creating files in the same directory
(``interfere" curve on \(y1\) axis) then the directory inode transitions out of
read caching and the first client must send \texttt{lookup()}s to the metadata
server (``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but performance suffers.  This degradation is shown in
Figure~\ref{fig:overhead-c}, where we scale the number of clients and show the
slowdown of the slowest client.  The results are normalized to a single
isolated client without a metadata server journal.  For the ``interfere" bars,
each client creates files in private directories and at 30 seconds we launch
another process that creates files in those directories. 18 clients is the
maximum number the metadata server could handle for this metadata-intensive
workload; at higher client load, the metadata server started complaining about
laggy and unresponsive requests.

>>>>

% CITE ME Lustre paralle
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many
creates, has the highest resource usage (combined CPU, network, and disk)
because of the number of RPCs needed for consistency and durability. The RPCs are
also serialized because the metadata server is single threaded; although naive,
this design is common because of the complexity of multi-threaded metadata
servers.  Traditional file system techniques for improving performance, such as
caching inodes, do not help for create-heavy workloads.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-journal.png}
      \caption{Runtime normalized to no journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.2\linewidth]{graphs/behavior-interfere.png}
      \caption{Interference forces \texttt{lookup()}s}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{Interference hurts variability}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{The overhead of global durability and strong consistency in CephFS.
  (a) shows the effect of different journal segment sizes, which are streamed
  into the object store for fault tolerance. (b) and (c) show that when a second
  client ``interferes", capabilities are revoked and metadata servers do more
  work.  \label{fig:overhead}}
\end{figure*}

% what is durability
While durability is not specified by POSIX IO, users expect that files they
create or modify survive failures.  We define three types of durability:
global, local, and none.  Global durability means that the client or server can
fail at any time and metadata will not be lost because it is ``safe" ({\it
i.e.} striped or replicated across a cluster). Local durability means that
metadata can be lost if the client or server stays down after a failure. None
means that metadata is volatile and that the system provides no guarantees when
clients or servers fail.  None is different than local durability because
regardless of the type failure, metadata will be lost when components die in a
None configuration.

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: a journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to grow large
(on the order of MBs) which ensures (1) sequential writes into the object store
and (2) the ability for daemons to trim redundant or irrelevant journal
entries.  The journal is striped over objects where multiple journal updates
can reside on the same object. There are two tunables for controlling the
journal: the segment size and the number of segments that can be written in
parallel. Unless the journal saturates memory or CPU resources, larger values
for these tunables results in better performance.

@@

% CITEME: SSTables
\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
to the best of our knowledge, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then, on restart,
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which
initially reside in memory but are later flushed to the underlying
distributed file system.

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:overhead-b}. The colors show the behavior of the client for two
different runs.  If only one client is creating files in a directory
(``isolated" curve on \(y1\) axis) then that client can lookup the existence of
new files locally before issuing a create request to the metadata server. If
another client starts creating files in the same directory (``interfere" curve
on \(y1\) axis) then the directory inode transitions out of read caching and
the first client must send \texttt{lookup()}s to the metadata server
(``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but performance suffers.  This degradation is shown in
Figure~\ref{fig:overhead-c}, where we scale the number of clients and show the
slowdown of the slowest client.  The results are normalized to a single
isolated client without a metadata server journal.  For the ``interfere" bars,
each client creates files in private directories and at 30 seconds we launch
another process that creates files in those directories. 18 clients is the
maximum number the metadata server could handle for this metadata-intensive
workload; at higher client load, the metadata server started complaining about
laggy and unresponsive requests.

### 2017-10-23 paper/sections/4_methodology.tex
paper: add patrick to authors and switch to POSIX IO
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: patrick feedback and spellcheck
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{figures/fig-decouple.png}
\caption{Applications decouple the namespace, write updates to a local journal,
and delay metadata updates using the Cudele Mechanisms }\label{fig:decouple}
\end{figure}

@@

In this section we describe Cudele, our API and framework that lets users
assign consistency and durability semantics to subtrees in the global
namespace. A \textbf{mechanism} is an abstraction and basic building block for
constructing consistency and durability guarantees. Cudele exposes these
mechanisms and the user composes them together to construct
\textbf{policies}. These policies are assigned to subtrees and they dictate how
the file system should handle operations within that subtree.  Below, we
describe the mechanisms, the policies, and the API for assigning policies to
subtrees.

@@

% describe the figure
Figure~\ref{fig:decouple} shows the mechanisms (labeled arrows) in Cudele and
which daemon(s) they are performed by.  Table~\ref{table:mechanisms} has a
description of what each mechanism does.  Decoupled clients use the ``Append Client Journal"
mechanism to append metadata updates to a local, in-memory journal. Once the
job is complete, the system calls Cudele mechanisms to achieve the desired
consistency/durability semantics.  Cudele provides a library for clients to
link into and all operations are performed by the client.

\subsubsection{Mechanisms Used for Consistency} ``RPCs" send remote procedure
calls for every metadata operation from the client to the metadata server,
assuming the request cannot be satisfied by the inode cache. This mechanism is
part of the default CephFS implementation and is the strongest form of
consistency because clients see metadata updates right away.  ``Nonvolatile
Apply" replays the client's journal onto the metadata cluster's metadata store.
The client's in-memory journal is written into the object store and the
metadata servers are restarted. When the metadata servers re-initialize, they
notice new journal updates in the object store and replay the events onto their
in-memory metadata stores.  ``Volatile Apply" takes the client's in-memory journal on the
client and applies the updates directly to the in-memory metadata store maintained
by the metadata servers. We say volatile because -- in exchange for peak
performance -- Cudele makes no consistency or durability guarantees while
``Volatile Apply" is executing.  If a concurrent update from a client occurs
there is no rule for resolving conflicts and if the client or metadata server
crashes there may be no way to recover.

% difference between apply and volatile apply
The biggest difference between ``Volatile Apply" and ``Nonvolatile Apply" is
the medium they use to communicate. ``Volatile Apply" applies updates directly
to the metadata servers' metadata store while ``Nonvolatile Apply" uses the
object store to communicate the journal of updates from the client to the
metadata servers.  ``Nonvolatile Apply" is safer but has a large performance
overhead because objects in the metadata store need to be read from and written
back to the object store.

%The metadata store and journal
%are different ways of representing the namespace.  Cudele presents 6
%mechanisms: RPCs, Stream, Create, Volatile Apply, Local Persist, and Global
%Persist. ``RPCs" does round trip remote procedure calls to establish
%consistency; it is the default implementation for complying with POSIX in
%CephFS. ``Stream" has the metadata servers stream a journal of metadata updates
%into the object store. ``Append Client Journal" allows clients to append metadata events to an
%in-memory journal. ``Volatile apply" 
% ``Local Persist" takes the in-memory journal and writes it to the
%client's disk. ``Global Persist" saves the journal as a an object in the object
%store from the client.  Next, we discuss how these mechanisms can be composed
%to get different consistency and durability semantics.

\subsubsection{Mechanisms Used for Durability} ``Stream" is one of the
mechanisms used by default in CephFS.  Using existing configuration settings in
Ceph we can turn ``Stream" on and off.  If it is off, then the metadata servers
will not save journals in the object store. For ``Local Persist", clients write
serialized log events to a file on local disk and for ``Global Persist",
clients push the journal into the objects store. The overheads for both ``Local
Persist" and ``Global Persist" is the write bandwidth of the local disk and
object store, respectively.  These persist mechanisms are part of the library that
links into the client.

@@

% describe table
The spectrum of consistency and durability guarantees that users can
construct is shown in Table~\ref{table:spectrum}. The columns are the different
consistency semantics and the rows cover the spectrum of durability guarantees.
For consistency: ``invisible" means the system does not handle merging updates
into a global namespace and it is assumed that middleware or the application
manages consistency lazily; ``weak" merges updates at some time in the
future ({\it e.g.}, when the system has time, when the number of updates reaches a
certain threshold, when the client is done writing, etc.); and updates in
``strong" consistency are seen immediately by all clients. For durability,
``none" means that updates are volatile and will be lost on a failure. Stronger
guarantees are made with ``local", which means updates will be retained if the
client node recovers, and ``global", where all updates are always recoverable.

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum}.  POSIX-compliant systems like CephFS and IndexFS
have global consistency and durability~\footnote{This is the normal case.
IndexFS also has bulk merge which would transition the system into ``weak
consistency"}; DeltaFS uses ``invisible" consistency and ``local" durability
and BatchFS uses ``weak" consistency and ``local" durability. These systems
have other features that could push them into different semantics but we assign
labels here based on the points emphasized in the papers.  To compose the
mechanisms users inject which mechanisms to run and which to use in parallel
using a domain specific language.  Although we can achieve all permutations of
the different guarantees in Table~\ref{table:spectrum}, not all of them make
sense. For example, it makes little sense to do \texttt{append client
journal+RPCs} since both mechanisms do the same thing or \texttt{stream+save}
since ``global" durability is stronger and has more overhead than ``local"
durability. The cost of each mechanism and the semantics described above are
quantified in Sections~\S\ref{sec:microbenchmarks} and~\S\ref{sec:use-case-1}.

% talk of eventual consistency
The consistency and durability properties in Table~\ref{table:spectrum} are not
guaranteed until all mechanisms in the cell are complete. The compositions
should be considered atomic and there are no guarantees while transitioning
between policies. For example, updates are not deemed to have ``global" durability until
they are safely saved in the object store. If a failure occurs during ``global
persist" or if we inject a new policy that changes a subtree from ``local
persist" to ``global persist", Cudele makes no guarantee until the mechanisms are
complete.

@@

% the interface
Users control consistency and durability for subtrees by contacting the monitor
daemon with a directory path and presenting a policies configuration file.
For example, (msevilla/mydir, policies.yml) would decouple the path
``msevilla/mydir" and would apply the policies in ``policies.yml".  The
policies file supports the following parameters (default values are in parenthesis):

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{figures/fig-decouple.png}
\caption{Applications decouple the namespace, write updates to a local journal,
and delay updates using the \textbf{mechanisms} shown here; they are described
in Table~\ref{table:mechanisms}.}\label{fig:decouple}
\end{figure}

@@

In this section we describe Cudele, our API and framework that lets users
assign consistency and durability semantics to subtrees in the global
namespace. A \textbf{mechanism} is an abstraction and basic building block for
constructing consistency and durability guarantees. Cudele exposes these
mechanisms and the user composes them together to construct \textbf{policies}.
These policies are assigned to subtrees and they dictate how the file system
should handle operations within that subtree.  Below, we describe the
mechanisms (which are \underline{underlined}), the policies, and the API for assigning
policies to subtrees.

@@

% describe the figure
Figure~\ref{fig:decouple} shows the mechanisms (labeled arrows) in Cudele and
which daemon(s) they are performed by.  Table~\ref{table:mechanisms} has a
description of what each mechanism does.  Decoupled clients use the
\underline{Append Client Journal} mechanism to append metadata updates to a
local, in-memory journal. This is fast because clients do not need to check for
consistency when writing events and the metadata server blindly applies the
updates because it assumes the events were already checked for consistency. The
trade-off here is performance; it is a dangerous approach but could be
implemented safely if the clients or metadata server are configured to check
the validity of events before writing them.  Once the job is complete, the
system calls Cudele mechanisms to achieve the desired consistency/durability
semantics.  Cudele provides a library for clients to link into and all
operations are performed by the client.

\subsubsection{Mechanisms Used for Consistency} \underline{RPCs} send remote procedure
calls for every metadata operation from the client to the metadata server,
assuming the request cannot be satisfied by the inode cache. This mechanism is
part of the default CephFS implementation and is the strongest form of
consistency because clients see metadata updates right away.  \underline{Nonvolatile
Apply} replays the client's journal onto the metadata cluster's metadata store.
The client's in-memory journal is written into the object store and the
metadata servers are restarted. When the metadata servers re-initialize, they
notice new journal updates in the object store and replay the events onto their
in-memory metadata stores.  \underline{Volatile Apply} takes the client's in-memory journal on the
client and applies the updates directly to the in-memory metadata store maintained
by the metadata servers. We say volatile because -- in exchange for peak
performance -- Cudele makes no consistency or durability guarantees while
Volatile Apply is executing.  If a concurrent update from a client occurs
there is no rule for resolving conflicts and if the client or metadata server
crashes there may be no way to recover.

% difference between apply and volatile apply
The biggest difference between Volatile Apply and Nonvolatile Apply is
the medium they use to communicate. Volatile Apply applies updates directly
to the metadata servers' metadata store while Nonvolatile Apply uses the
object store to communicate the journal of updates from the client to the
metadata servers.  Nonvolatile Apply is safer but has a large performance
overhead because objects in the metadata store need to be read from and written
back to the object store.

%The metadata store and journal
%are different ways of representing the namespace.  Cudele presents 6
%mechanisms: RPCs, Stream, Create, Volatile Apply, Local Persist, and Global
%Persist. ``RPCs" does round trip remote procedure calls to establish
%consistency; it is the default implementation for complying with POSIX IO in
%CephFS. ``Stream" has the metadata servers stream a journal of metadata updates
%into the object store. ``Append Client Journal" allows clients to append metadata events to an
%in-memory journal. ``Volatile apply" 
% ``Local Persist" takes the in-memory journal and writes it to the
%client's disk. ``Global Persist" saves the journal as a an object in the object
%store from the client.  Next, we discuss how these mechanisms can be composed
%to get different consistency and durability semantics.

\subsubsection{Mechanisms Used for Durability} \underline{Stream} is one of the
mechanisms used by default in CephFS.  Using existing configuration settings in
Ceph we can turn Stream on and off.  If it is off, then the metadata servers
will not save journals in the object store. For \underline{Local Persist}, clients write
serialized log events to a file on local disk and for \underline{Global Persist},
clients push the journal into the objects store. The overheads for both Local
Persist and Global Persist is the write bandwidth of the local disk and
object store, respectively.  These persist mechanisms are part of the library that
links into the client.

@@

% describe table
The spectrum of consistency and durability guarantees that users can construct
is shown in Table~\ref{table:spectrum}. The columns are the different
consistency semantics and the rows cover the spectrum of durability guarantees.
For consistency: ``invisible" means the system does not handle merging updates
into a global namespace and it is assumed that middleware or the application
manages consistency lazily; ``weak" merges updates at some time in the future
({\it e.g.}, when the system has time, when the number of updates reaches a
certain threshold, when the client is done writing, etc.); and updates in
``strong" consistency are seen immediately by all clients. For durability,
``none" means that updates are volatile and will be lost on a failure. Stronger
guarantees are made with ``local", which means updates will be retained if the
client node recovers and reads the updates from local storage, and ``global",
where all updates are always recoverable.

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum}.  POSIX IO-compliant systems like CephFS and IndexFS
have global consistency and durability~\footnote{This is the normal case.
IndexFS also has bulk merge which would transition the system into ``weak
consistency"}; DeltaFS uses ``invisible" consistency and ``local" durability
and BatchFS uses ``weak" consistency and ``local" durability. These systems
have other features that could push them into different semantics but we assign
labels here based on the points emphasized in the papers.  To compose the
mechanisms users inject which mechanisms to run and which to use in parallel
using a domain specific language.  Although we can achieve all permutations of
the different guarantees in Table~\ref{table:spectrum}, not all of them make
sense. For example, it makes little sense to do \texttt{append client
journal+RPCs} since both mechanisms do the same thing or \texttt{stream+save}
since ``global" durability is stronger and has more overhead than ``local"
durability. The cost of each mechanism and the semantics described above are
quantified in Sections~\S\ref{sec:microbenchmarks} and~\S\ref{sec:use-case-1}.

% talk of eventual consistency
The consistency and durability properties in Table~\ref{table:spectrum} are not
guaranteed until all mechanisms in the cell are complete. The compositions
should be considered atomic and there are no guarantees while transitioning
between policies. For example, updates are not deemed to have ``global"
durability until they are safely saved in the object store. If a failure occurs
during Global Persist or if we inject a new policy that changes a subtree from
Local Persist to Global Persist, Cudele makes no guarantee until the mechanisms
are complete. Despite this, production systems that use Cudele should state
up-front what the transition guarantees are for subtrees.

@@

% the interface
Users control consistency and durability for subtrees by contacting a daemon in
the system called a monitor, which manages cluster state changes.  Users
present a directory path and a policies configuration that gets distributed and
versioned by the monitor to all daemons in the system. For example,
(msevilla/mydir, policies.yml) would decouple the path ``msevilla/mydir" and
would apply the policies in ``policies.yml".  The policies file supports the
following parameters (default values are in parenthesis):

### 2017-10-23 paper/sections/6_results.tex
paper: patrick feedback and spellcheck
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{[\href{https://www.google.com}{source}] Microbenchmark: performance of each
mechanism (left) and building consistency/durability guarantees (right) for
100K files on a single client. Results are normalized to the runtime of writing
files creates to the client's in-memory journal.
\label{fig:composable-mechanisms}}
\end{figure}

@@

{\it Journal Size:} We measure the amount of storage per journal update to be
about 2.5\text{KB}. The storage footprint scales linearly with the number of
metadata creates and suggests that updates for a million files would be 2.5KB
\(*\) 1 million files \(=\) 2.38GB. Transfer times for payloads of this size in
most HPC/data cente networks are reasonable.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Use Case 2}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Use Case 3}
      \label{fig:slowdown-sync}
  \end{subfigure}
\caption{The performance and features of Cudele. (a) shows the cost of
merging client journals at the metadata server. Merging is better than RPCs
because there are less messages and consistency/durability code paths are
bypassed. In (b), the allow/block API isolates directories from interfering
clients. (c) is the slowdown of a single client syncing updates to the gobal
namespace. The inflection point is the trade-off of frequent updates vs. larger
journal files.\label{fig:use-cases}}
\end{figure*}

% CITEME xiao:socc2015-shardfs CITEME HADOOP
Clients creating files in private directories is heavily studied in
HPC~\cite{weil:sc2004-dyn-metadata, ren:sc2014-indexfs, patil:fast2011-giga,
zheng:pdsw2014-batchfs, sevilla:sc15-mantle}, mostly due to
checkpoint-restart~\cite{bent_plfs_2009}.  But the workload also appears in
cloud workloads, where systems like Hadoop use the file abstraction to exchange
work units to workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  We use this as a microbenchmark because it
allows us to control the size of the log, since each create creates a single
journal event. The workload is clients creating 100K files in private
directories in the same global namespace.

@@

\subsection{Use Case 2: Creates with Interferring Client}

@@

Figure~\ref{fig:block-allow} plots the overhead of the slowest client and the
error bars are the standard deviation of 3 runs.  ``Interfere (Fig 3c)" is the
result from Figure~\ref{fig:overhead-b}; ``Interfere" uses the allow/block API
to return \texttt{-EBUSY} to interferring clients; and ``Isolated" is the
baseline performance without an interferring Each subtree has ``RPCs" and
``Stream" enabled.  Results results are normalized to the runtime of a single
client creating files in a directory. Note that IndexFS has a similar behavior
to ``interfere" with leases, except clients block.

@@

% CITEME
Scientists use the file system to check the progress of jobs using
\texttt{ls}~\cite{CITEME}. The number of files or size of the files is
indicative of the progress. This practice is not too different from systems
that use the file system to manage the progress of jobs; Hadoop writes to
temporary files, renames them when complete, and creates a ``DONE" file to
indicate to the runtime that the task did not fail and should not be
re-scheduled on another node. In this scenario, Cudele users will not see the
progress of decoupled namespaces since their updates are not globally visible.
To help scientists judge the progress of their jobs, Cudele clients have a
``namespace sync" that sends batches of updates back to the global namespace at
regular intervals.

@@

Cudele and the experiments we present here prompt many avenues for future work.
First is quantifying the benefits of dynamically changing the semantics of a
subtree from stronger to weaker guarantees (or vice versa), as described in the
introduction. Second is embeddable policies, where child subtrees have
specialized features but still maintain the guarantees  of their parent
subtrees. We already show how applciations can compose guarantees and control
their performance, knobs that we did not have before, but embeddable policies
are a way to compose the policies themsleves.  For example, a RAMDisk subtree
is POSIX IO-compliant but relaxes durability constraints, so it can reside
under a POSIX IO subtree that is strongly consistent. These embeddable policies
should be controlled and enforced by Cudele.  Finally, performance prediction
benefits from our cost quantification of each mechanism. Applications can use
Cudele to microbenchmark their components and software, similar to what we did
in Secion~\S\ref{sec:microbenchmarks}. Using those results, they can predict
how much slower their system will be if they adopt stronger consistency or
durability.  This is a form of co-design that takes a ``dirty-slate" approach
but building just the guarantees the application needs from existing
implementations.  This can also be a verification tool where performance that
varies wildly from the predicted performance can be a red flag that something
is wrong or that the bottleneck is not in the consistency or durability plane.

>>>>

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{[\href{https://www.google.com}{source}] Performance of each
mechanism (left) and building consistency/durability guarantees (right) for
100K files creates from a single client. Results are normalized to the runtime of writing
events to the client's in-memory journal.
\label{fig:composable-mechanisms}}
\end{figure}

@@

{\it Journal Size:} We measure the amount of storage per journal update to be
about 2.5\text{KB}. The storage footprint scales linearly with the number of
metadata creates and suggests that updates for a million files would be 2.5KB
\(*\) 1 million files \(=\) 2.38GB. Transfer times for payloads of this size in
most HPC/data center networks are reasonable.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Use Case 2}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Use Case 3}
      \label{fig:slowdown-sync}
  \end{subfigure}
\caption{The performance and features of Cudele. (a) shows the cost of
merging client journals at the metadata server. Merging is better than RPCs
because there are less messages and consistency/durability code paths are
bypassed. In (b), the allow/block API isolates directories from interfering
clients. (c) is the slowdown of a single client syncing updates to the global
namespace. The inflection point is the trade-off of frequent updates vs. larger
journal files.\label{fig:use-cases}}
\end{figure*}

% CITEME xiao:socc2015-shardfs CITEME HADOOP
First we show how we can build application-specific subtrees by composing
mechanisms and that this approach results in more a scalable global
namespace. We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
But the workload also appears in cloud workloads, where systems like Hadoop use
the file abstraction to exchange work units to workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  We use this as a microbenchmark because it
allows us to control the size of the log, since each create creates a single
journal event. The workload is clients creating 100K files in private
directories in the same global namespace.

@@

\subsection{Use Case 2: Creates with Interfering Client}

@@

Figure~\ref{fig:block-allow} plots the overhead of the slowest client and the
error bars are the standard deviation of 3 runs.  ``Interfere (Fig 3c)" is the
result from Figure~\ref{fig:overhead-b}; ``Interfere" uses the allow/block API
to return \texttt{-EBUSY} to interfering clients; and ``Isolated" is the
baseline performance without an interfering. Each subtree has ``RPCs" and
``Stream" enabled.  Results results are normalized to the runtime of a single
client creating files in a directory. Note that IndexFS has a similar behavior
to ``interfere" with leases, except clients block.

@@

% CITEME
The final use case shows how the API gives users fine-grained control of the
consistency semantics for niche or {\it ad-hoc} workflows.  Scientists use the
file system to check the progress of jobs using \texttt{ls}~\cite{CITEME}. The
number of files or size of the files is indicative of the progress. This
practice is not too different from systems that use the file system to manage
the progress of jobs; Hadoop writes to temporary files, renames them when
complete, and creates a ``DONE" file to indicate to the runtime that the task
did not fail and should not be re-scheduled on another node. In this scenario,
Cudele users will not see the progress of decoupled namespaces since their
updates are not globally visible.  To help scientists judge the progress of
their jobs, Cudele clients have a ``namespace sync" that sends batches of
updates back to the global namespace at regular intervals.

@@

Cudele and the experiments we present here prompt many avenues for future work.
First is quantifying the benefits of dynamically changing the semantics of a
subtree from stronger to weaker guarantees (or vice versa), as described in the
introduction. Second is embeddable policies, where child subtrees have
specialized features but still maintain the guarantees  of their parent
subtrees. We already show how applications can compose guarantees and control
their performance, knobs that we did not have before, but embeddable policies
are a way to compose the policies themselves.  For example, a RAMDisk subtree
is POSIX IO-compliant but relaxes durability constraints, so it can reside
under a POSIX IO subtree that is strongly consistent. These embeddable policies
should be controlled and enforced by Cudele.  Finally, performance prediction
benefits from our cost quantification of each mechanism. Applications can use
Cudele to microbenchmark their components and software, similar to what we did
in Section~\S\ref{sec:microbenchmarks}. Using those results, they can predict
how much slower their system will be if they adopt stronger consistency or
durability.  This is a form of co-design that takes a ``dirty-slate" approach
but building just the guarantees the application needs from existing
implementations.  This can also be a verification tool where performance that
varies wildly from the predicted performance can be a red flag that something
is wrong or that the bottleneck is not in the consistency or durability plane.
